### 2014-12-10 stat343/final.tex
Added in R code for question 2b

                        We see that they all fall outside of the critical values for all confidence levels, so we would reject them all as outliers for all confidence levels.
                        Using the method described above, once again for 2000 total boots, but this time for studentized residuals, I have once again plotted the critical values. The same issue for critical values close to 0 exists.
                            \includegraphics[width=9cm]{final/2bii_plot} 
                        Comparing the $1$st-$10$th studentized residuals from the original model:\\ 
                        \lstinputlisting[firstline=44,lastline=45]{final/2_out.txt} 
                        \lstinputlisting[firstline=47,lastline=50]{final/2_out.txt} 
                        We see that they all fall outside of the critical values for all confidence levels, so we would reject them all as outliers for all confidence levels. This fits with the simpler Bonferroni Critical value we used before; since it is conservative, and each of these falls above it, it stands to reason a sharper test would reject them to.

>>>>

                        We see that they all fall outside of the critical values for all confidence levels, so we would reject them all as outliers for all confidence levels. \\
                        {\bf My R Code:}
                        \lstinputlisting[firstline=191,lastline=214,breaklines=true]{final.R}

                    \item[ii.]
                        Using the method described above, once again for 2000 total boots, but this time for studentized residuals, I have once again plotted the critical values. The same issue for critical values close to 0 exists.
                        \begin{center}
                            \includegraphics[width=9cm]{final/2bii_plot} 
                        \end{center}
                        Comparing the $1$st-$10$th studentized residuals from the original model:\\ 
                        \lstinputlisting[firstline=44,lastline=45]{final/2_out.txt} 
                        To the respective critical values: \\
                        \lstinputlisting[firstline=47,lastline=50]{final/2_out.txt} 
                        We see that they all fall outside of the critical values for all confidence levels, so we would reject them all as outliers for all confidence levels. This fits with the simpler Bonferroni Critical value we used before; since it is conservative, and each of these falls above it, it stands to reason a sharper test would reject them to. \\
                        {\bf My R Code:}
                        \lstinputlisting[firstline=231,lastline=247,breaklines=true]{final.R}
